`Big data' og politologisk datavidenskab

### 2020-03-28 draft_v01.tex
new knit

\emph{Levels of analysis and measurement}

>>>>

\emph{Levels of analysis and measurements on big data}

Theories in empirical political science come with a \emph{level of
analysis}. For example, a theory about party behavior during election
campaigns has a party-election level of analysis: each party at each
election is one observation. A theory about politicians during election
campaigns gives a necessarily larger number of observations per
election, since each individual politician during a campaign is one
observation. It is relatively rare in political science to express our
theories at the level of granularity in most big data sets. It is, of
course, entirely possible to develop a theory to explain individual
tweets or individual laws, etc., but political science generally
expresses its theories at a higher level (less granular) level of
analysis.

In the next section, we introduce several popular and useful methods for
working with big data. As we will see, these methods specifically
associated with big data have in common that they are actually
measurement tools. We will look at methods for labeling data,
discovering patterns, and condensing large amounts of data into simpler,
smaller data. It is typical for political scientists applying big data
that their ``big'' data set of a million tweets or thousands of laws
condenses into a data set of, for example, thousands of politician-month
observations or hundreds of government-year observations.

The workhorse method of observational, quantitative hypothesis-testing
in political science, even when working with big data, remains to build
and estimate appropriate statistical models with appropriate control
variables. Thus, we will focus on the methodological choices that
distinguish analyses using big data from the more familiar social
science workflow of building a purpose-built data set arranged at the
correct level of analysis. Readers who are familiar with qualitative
methods will be more familiar with this pattern. For example, lengthy
interviews or wide-ranging case studies are often condensed into a
summary coding of theoretical concepts.

This raises a point worth emphasizing about big data methods in
political science. Although methods for working with big data are,
necessarily, computational they do not necessarily mean that researchers
must apply quantitative methodology in their overall research design.
